An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-20 EconGrowth-R-Functions.Rnw
Beginning the work on the lattice version of the triangle plot that contains (a) all the relevant energy parameters and their confidence intervals (on the y axis) and (b) the values of the parameters (on the x axis).

  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}

@@

  else if (model == "CESe"){data <- cesParamsTableDF(energyType)}

@@

    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be.")

@@

# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
# for each country.
# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
# param the parameter you want to plot. The options depend upon the model you want:
#       SF: lambda or m
#       CD: lambda, alpha, or beta
#      CDe: lambda, alpha, beta, or gamma
#      CES: gamma, lambda, delta_1, sigma_1, or delta
#     CESe: gamma, lambda, delta_1, sigma_1, delta, or sigma
#    LINEX: a_0 or c_t
# energyType the energy type you want. One of Q, X, or U
# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
# textScaling the scale factor for labels on the graph
CIvsParamPlot <- function(model, param, energyType=NA, factor=NA, textScaling=1.0){
  data <- CIvsParamDF(model=model, param=param, energyType=energyType, factor=factor)
    xLabel <- "$\\lambda$ [1/year]"
    xLimits <- c(0.0, 0.1); atX=c(0.0, 0.05, 0.1)
    yLimits <- c(0.0, 0.2); atY-c(0.0, 0.1, 0.2)
    if (factor == "K"){xLabel <- "$\\alpha$"}
    else if (factor == "L"){xLabel <- "$\\beta$"}
    else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
    xLimits <- c(-0.1, 1.5); atX <- c(0.0, 0.5, 1.0, 1.5)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
    xLabel <- "$\\alpha$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
    xLabel <- "$\\beta$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
    xLabel <- "$\\gamma$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
    xLabel <- "$\\delta_1$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
    xLabel <- "$\\sigma_1$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 2.0); atY <- c(0.0, 1.0, 2.0)
    xLabel <- "$\\delta$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
    xLabel <- "$\\sigma$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
    xLabel <- "$a_0$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
    xLabel <- "$c_t$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  yLabel <- paste("Width of 95\\% CI on", xLabel)
  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CI width
                 xlab=list(label=xLabel),
                 ylab=list(label=yLabel),
                             x=list(at=atX),
                             y=list(at=atY)
                 xlim=xLimits, #x axis limits
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=rownames(data))
                 })
  return(plot)

>>>>

  else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType=energyType)}

@@

  else if (model == "CESe"){data <- cesParamsTableDF(energyType=energyType)}

@@

    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be!")

@@

#######################
# Creates a plot of confidence interval vs. value of a parameter with symbols being the 2-letter abbreviation
# for each country.
# 
# model the model function you want to use. One of SF, CD, CDe, CES, or LINEX.
# param the parameter you want to plot. The options depend upon the model you want:
#       SF: lambda or m
#       CD: lambda, alpha, or beta
#      CDe: lambda, alpha, beta, or gamma
#      CES: gamma, lambda, delta_1, sigma_1, or delta
#     CESe: gamma, lambda, delta_1, sigma_1, delta, or sigma
#    LINEX: a_0 or c_t
# energyType the energy type you want. One of Q, X, or U
# factor the factor you want to use in a single-factor model, if needed. One of K, L, Q, X, or U.
# textScaling the scale factor for labels on the graph
##
CIvsParamPlot <- function(model, param, energyType=NA, factor=NA, textScaling=1.0){
  # Get the data from the requested model
  data <- CIvsParamDF(model=model, param=param, energyType=energyType, factor=factor)
  # Also, set limits on the x and y axes if needed
  if (param == "lambda"){
    xLabel <- "$\\lambda$ [1/year]"
    xLimits <- c(0.0, 0.1); atX=c(0.0, 0.05, 0.1)
    yLimits <- c(0.0, 0.2); atY-c(0.0, 0.1, 0.2)
  } else if (param == "m"){
    if (factor == "K"){xLabel <- "$\\alpha$"}
    else if (factor == "L"){xLabel <- "$\\beta$"}
    else if ((factor == "Q") || (factor == "X") || (factor == "U")){xLabel <- "$\\gamma$"}
    xLimits <- c(-0.1, 1.5); atX <- c(0.0, 0.5, 1.0, 1.5)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  } else if (param == "alpha"){
    xLabel <- "$\\alpha$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  } else if (param == "beta"){
    xLabel <- "$\\beta$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  } else if (param == "gamma"){
    xLabel <- "$\\gamma$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
  } else if (param == "delta_1"){
    xLabel <- "$\\delta_1$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  } else if (param == "sigma_1"){
    xLabel <- "$\\sigma_1$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 2.0); atY <- c(0.0, 1.0, 2.0)
  } else if (param == "delta"){
    xLabel <- "$\\delta$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
  } else if (param == "sigma"){
    xLabel <- "$\\sigma$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(-0.1, 2.0); atY <- c(0.0, 1.0, 2.0)
  } else if (param == "a_0"){
    xLabel <- "$a_0$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  } else if (param == "c_t"){
    xLabel <- "$c_t$"
    xLimits <- c(-0.1, 1.1); atX <- c(0.0, 0.5, 1.0)
    yLimits <- c(0.0, 1.5); atY <- c(0.0, 0.5, 1.0, 1.5)
  }
  yLabel <- paste("Width of 95\\% CI on", xLabel)

  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CI width
                 xlab=list(label=xLabel),
                 ylab=list(label=yLabel),
                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
                             x=list(at=atX),
                             y=list(at=atY)
                             ), 
                 xlim=xLimits, #x axis limits
                 ylim=yLimits, #y axis limits
                 panel = function(x, y){
                   ltext(x=x, y=y, labels=rownames(data))
                 })
  return(plot)
}

########################
# Creates a lattice plot that has the size of confidence intervals on the vertical axis and parameter
# values on the horizontal axis.
# At this point, this function is NOT a general-purpose function, as the number of permutations
# of model, parameter, energy type, and factor is too varied to be able to turn into a general-purpose 
# graph with little time investment at this point.
# This function makes a lattice plot with the following panels (in the arrangement shown)
#
# gammaCDeq   gammaCDex    gammaCDeu
# deltaCESeq  deltaCESex   deltaCESeu
# sigmaCESeq  sigmaCESex   sigmaCESeu
#
# Parameters and models (gamma for CDe and delta and sigma for CESe) are in rows and energyTypes (q, x, and u) 
# are in columns.
##
CIvsParamLattice <- function(descriptors){
  # Build a data.frame that has all the necessary models
  gammaCDeqDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="Q")
  gammaCDexDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="X")
  gammaCDeuDF  <- CIvsParamDF(model="CDe",  param="gamma", energyType="U")
  deltaCESeqDF <- CIvsParamDF(model="CESe", param="delta", energyType="Q")
  deltaCESexDF <- CIvsParamDF(model="CESe", param="delta", energyType="X")
  deltaCESeuDF <- CIvsParamDF(model="CESe", param="delta", energyType="U")
  sigmaCESeqDF <- CIvsParamDF(model="CESe", param="sigma", energyType="Q")
  sigmaCESexDF <- CIvsParamDF(model="CESe", param="sigma", energyType="X")
  sigmaCESeuDF <- CIvsParamDF(model="CESe", param="sigma", energyType="U")
  # Change the name of the first columns (the ones that contain the parameter of interest to us) to "param".
  # Doing this allows us to combine the individual data frames into one large data frame.
  colnames(gammaCDeqDF)[1]  <- "param"
  colnames(gammaCDexDF)[1]  <- "param"
  colnames(gammaCDeuDF)[1]  <- "param"
  colnames(deltaCESeqDF)[1] <- "param"
  colnames(deltaCESexDF)[1] <- "param"
  colnames(deltaCESeuDF)[1] <- "param"
  colnames(sigmaCESeqDF)[1] <- "param"
  colnames(sigmaCESexDF)[1] <- "param"
  colnames(sigmaCESeuDF)[1] <- "param"
  # Create one big data.frame with all of the data.
  data <- rbind(gammaCDeqDF,  gammaCDexDF,  gammaCDeuDF, 
                deltaCESeqDF, deltaCESexDF, deltaCESeuDF, 
                sigmaCESeqDF, sigmaCESexDF, sigmaCESeuDF)
  # Now make the graph.
}
@
